---
title: "Flu Scenario Modelling"
output:
  html_document:
    code_folding: show
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
editor_options: 
  chunk_output_type: console
  chunk_output_highlight: default
---

# Flu Scenario Modelling-repeat update

```{r}
load(file = "./output/rep_list.Rdata") # rep_list
rl = rep_list
```

## Executive summary

We fit a flu scenario model (deterministic SIR, age- and vaccine-status disaggregated) to ILI-plus as an indicator of flu activity. The model is fitted separately to all `r rl$N_countries_fit` EU/EEA countries that have data. \
\
-Highlights of any countries where recent ILI activity deviates significantly from expectations\
-overview over the scenario projections, and any substantial changes since the last report

```{r for_summary}

```

### Data overview

The date of the last data load is XXX, and the countries that indicated any activity where XXX.

Countries with most ILI activity added (compared to country-baseline):

### ILI-plus activity summary

Watch list of countries where ILI activity is unexpected based on the model's projections

### Scenario Projections

Summary table of what is projected for each country

```{r scenario_projections}
rl$sum_ili
```

### Methodology

Brief summary of the model structure

List of key assumptions and limitations

Explain analysis steps for this report

```{r }
# 

```
